Developing a preprint culture in biology

### 2012-10-05 ms.tex
Minor edits on the peerj section

PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new publishing system
that combines both a preprint server, and a peer reviewed journal.  It is
focused on the biological and medical sciences, which may help overcome the
perception that preprints do not have a home in biology.  PeerJ allows
commenting on posted preprints, improving the potential for pre-publication
dialog. In addition, preprints can be made private if the authors choose, and
shared only with selected colleagues. While this reduces some of the benefits of
preprints described above, it may allow some researchers who would not otherwise
post preprints to begin to explore the possibility in a manner appropriate to
their current circumstances.

In contrast to other preprint servers users cannot post unlimited public
preprints for free. One preprint per year can be posted for free and a onetime
(i.e. lifetime) fee of 99 dollars allows the posting of unlimited public
preprints. It is also worth noting that the preprint server is not tied to the
journal, so preprints can be posted regardless of where they will eventually be
submitted for publication.

>>>>

PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new publishing system
that combines both a preprint server, and a peer reviewed journal.  It is
focused on the biological and medical sciences, which may help overcome the
perception that preprints do not have a home in biology.  PeerJ allows
commenting on posted preprints, improving the potential for pre-publication
dialog. In addition, preprints can be made private if the authors choose, and
shared only with selected colleagues. While this reduces many of the benefits of
preprints described above, it may allow some researchers who would not otherwise
post preprints to begin to explore the possibility in a manner appropriate to
their current circumstances.

In contrast to other preprint servers users cannot post unlimited public
preprints for free. One preprint per year can be posted for free and a onetime
(i.e. lifetime) fee of 99 dollars allows the submitting author to post unlimited public
preprints. It is also worth noting that the preprint server is not tied to the
journal, so preprints can be posted regardless of where they will eventually be
submitted for publication.
